Through the eyes of the teacher

### 2021-02-04 paper_1/paper_1_supplement.Rmd
added table GRI

# prepare data (selected from questionnaire data)
et.raw.data<-read.table("./data/Aperol_pilot_02_glasses_fixation_metrics.tsv", dec=",", sep="\t", header=T)

# calculate GRI

# create a basic table (tibble) using tidyverse functions
et.quest.table <- et.raw.data %>%
  summarise("M Fixation Number" = round(mean(Number_of_whole_fixations), 2),
            "SE Fixation Number" = round(se(Number_of_whole_fixations), 2),
            "M Duration Fixation" = round(mean(Total_duration_of_whole_fixations)),
            "SE Duration Fixation" = round(se(Total_duration_of_whole_fixations))
            )

# format and insert table in manuscript
apa_table(
  et.quest.table,
  caption = "Number and Duration of fixations",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

>>>>

# prepare data (selected from questionnaire data)
et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)

# converting to integer to numeric
et.raw.data <- et.raw.data %>%  mutate(Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations))

# calculate GRI 
view(et.raw.data)

# create a basic table (tibble) using tidyverse functions
et.raw.table <- et.raw.data %>%
  group_by(Participant, Variable) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "M Duration Fixation" = mean(Total_duration_of_whole_fixations),
            "SE Duration Fixation" = round(se(Total_duration_of_whole_fixations, na.rm = TRUE), 2),
            "GRI" = round(mean(Total_duration_of_whole_fixations) / Number_of_whole_fixations)
            )

# format and insert table in manuscript
apa_table(
  et.raw.table,
  caption = "Number and Duration (in msec) of Fixations",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

### 2021-02-04 paper_1/paper_1_supplement.tex
added table GRI

@@

\caption{\label{tab:GRItable}Number and Duration of fixations}

@@

\begin{tabular}{llll}
\toprule
M Fixation Number & \multicolumn{1}{c}{SE Fixation Number} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{SE Duration Fixation}\\
\midrule
842.50 & 146.69 & 382,411.00 & 95,132.00\\
\bottomrule
\end{tabular}

@@

The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz and Rädiker (2019)). Therefore, a coding scheme was

>>>>

\begin{verbatim}
## # A tibble: 8 x 6
## # Groups:   Participant [8]
##   Participant Variable `Fixation Number` `M Duration Fix~ `SE Duration Fi~   GRI
##   <chr>       <chr>                <dbl>            <dbl>            <dbl> <dbl>
## 1 01_01_D     Expert                 803           316571               NA   394
## 2 01_02_A     Expert                1070           385812               NA   361
## 3 01_03_B     Novice                 617           374315               NA   607
## 4 01_04_C     Novice                 769           384537               NA   500
## 5 02_01_A     Novice                 569           101541               NA   178
## 6 02_02_B     Novice                1140           520431               NA   457
## 7 02_03_C     Novice                1048           469018               NA   448
## 8 02_04_D     Novice                 613           438655               NA   716
\end{verbatim}

@@

\caption{\label{tab:GRItable}Number and Duration (in msec) of Fixations}

@@

\begin{tabular}{llllll}
\toprule
Participant & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{SE Duration Fixation} & \multicolumn{1}{c}{GRI}\\
\midrule
01\_01\_D & Expert & 803.00 & 316,571.00 & NA & 394.00\\
01\_02\_A & Expert & 1,070.00 & 385,812.00 & NA & 361.00\\
01\_03\_B & Novice & 617.00 & 374,315.00 & NA & 607.00\\
01\_04\_C & Novice & 769.00 & 384,537.00 & NA & 500.00\\
02\_01\_A & Novice & 569.00 & 101,541.00 & NA & 178.00\\
02\_02\_B & Novice & 1,140.00 & 520,431.00 & NA & 457.00\\
02\_03\_C & Novice & 1,048.00 & 469,018.00 & NA & 448.00\\
02\_04\_D & Novice & 613.00 & 438,655.00 & NA & 716.00\\
\bottomrule
\end{tabular}

@@

The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz and Rädiker (2019)). The following coding scheme has been developed for coding:
